%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Backend Software Engineer} % Job title
    {Sympower} % Organization
    {Amsterdam, NL - Full remote} % Location
    {Nov. 2024 - Present} % Date(s)
    {
        Developing backend microservices using Kotlin and Spring Boot within a distributed international team. Initially contributed to the domain team managing the "Resource" abstraction layer, a critical component leveraged by all business teams across the company. Currently focused on developing solutions for Commercial \& Industrial (C\&I) assets in continental Europe.
        \begin{itemize}
            \item {Languages \& Frameworks: Kotlin, Java, Spring Boot}
            \item {Testing: JUnit, Mockito, Testcontainers, Cucumber}
            \item {Infrastructure \& Cloud: Docker, Kubernetes, Git}
            \item {Data \& Messaging: PostgreSQL, Pulsar}
        \end{itemize}
    }

%---------------------------------------------------------
    \cventry
    {Senior Backend Software Engineer} % Job title
    {Milkman Technologies} % Organization
    {Verona (VR), Italy - Full remote} % Location
    {Jan. 2024 - Nov. 2024} % Date(s)
    {
        Developed and maintained Spring Boot microservices for logistics route planning and monitoring systems. Designed and implemented new features across existing and new microservices integrating with distributed systems.
        \begin{itemize}
            \item {Languages \& Frameworks: Java 21, Spring Boot, Hibernate}
            \item {Testing: JUnit, Mockito}
            \item {Infrastructure \& Cloud: Docker, Kubernetes, AWS, Keycloak, Git}
            \item {Data \& Messaging: Kafka, PostgreSQL, MongoDB}
        \end{itemize}
    }

%---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {I-Tel S.r.l. | Maps Group} % Organization
    {Riccione (RN), Italy - On site} % Location
    {Mar. 2016 - Jan. 2024} % Date(s)
    {
        Evolved from junior developer to technical lead managing a healthcare focused development team and coordinating multiple projects. Designed and implemented distributed microservices for healthcare platforms and telemedicine applications driving the company's transition from a monolithic system to cloud distributed architecture. Led backend development initiatives, mentored colleagues and managed client relationships.
        \begin{itemize}
            \item {Languages \& Frameworks: Java (8-17), JavaScript, Spring Boot, Hibernate, Android}
            \item {Infrastructure \& Cloud: Docker, Kubernetes, GCP, Keycloak, Nginx, Tomcat, Git, SVN}
            \item {Data \& Messaging: PostgreSQL, Redis, FHIR}
        \end{itemize}
    }

%---------------------------------------------------------


\end{cventries}
